Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-24 DGMM2025/paper.tex
Working on 4

    \section{Feature-aware normal estimation and curvature estimation on digital surfaces}

    \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
    We propose a new normal estimator on digital surfaces, which uses
    the visibility of the point of interest while taking into account
    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
    average length between visible points (so some $c\sqrt{h}$ for $c$
    some constant), then this estimator is observed to be multigrid
    convergent along digitization of smooth shapes. However, since the
    computation window is limited by the visibility, it better
    approximates the geometry near sharp or salient features.

@@

    Then, to compute the curvatures, we use the Corrected Normal Current
    estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
    above.

>>>>

    \section{Saliency-aware normal and curvature estimation}

    \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
    \paragraph*{Saliency-aware normal estimator.}
    We propose a new normal estimator on digital surfaces, which uses
    the visibility of the point of interest while taking into account
    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
    average length between visible points (so some
    $\Theta(\sqrt{h})$), then this estimator is observed to be
    multigrid convergent along digitization of smooth shapes. However,
    since the computation window is limited by the visibility, it
    better approximates the geometry near sharp or salient features.

@@

    \paragraph*{Experimental convergence of normal estimation.}
    [TODO] Show normal estimations along smooth shapes and compare with Integral Invariant.

    \paragraph*{Application to curvature estimation.}
    Then, to compute the curvatures, we use the Corrected Normal
    Current estimator~\cite{lachaud:2022-dcg} which are based on the
    normals computed above.
